---
title: "Detect synthetic random collective events"
output: 
  rmarkdown::html_vignette:
    toc: true 
vignette: >
  %\VignetteIndexEntry{Detect synthetic random collective events}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = F, warning=FALSE}
library(ARCOS, quietly = T)
library(data.table, quietly = T)
library(ggplot2, quietly = T)
library(ggthemes, quietly = T)

lPar = list()

lPar$dirCore = "."
lPar$dirFramesOut = "output-frames"
lPar$saveFrames = TRUE

# Colour palette used for plotting
myColPal = ggthemes::tableau_color_pal(palette = "Tableau 20")(20)

# Custom plotting function
myPlotBinTS <- function(objTS,
                        colorVar,
                        colorPal = c("grey80",
                                     "grey20"),
                        legendPos = "none",
                        xlim = c(0,65), 
                        ylim = c(65,0),
                        ncol = 4,
                        plotType = c("raster", "point", "tile"),
                        pointSize = 1) {
  
  locFrame = attr(objTS, "colFrame")
  locPos = attr(objTS, "colPos")
  
  locP = ggplot(objTS,
                aes(x = get(locPos[1]),
                    y = get(locPos[2])))
  
  if (plotType == "point") {
    locP = locP +
      geom_point(aes(color = as.factor(get(colorVar))), size = pointSize) +
      scale_color_manual(name = "ID", values = colorPal)
  } else if (plotType == "raster") {
    locP = locP +
      geom_raster(aes(fill = as.factor(get(colorVar)))) +
      scale_fill_manual(name = "ID", values = colorPal)
  } else if (plotType == "tile") {
    locP = locP +
      geom_tile(aes(fill = as.factor(get(colorVar)))) +
      scale_fill_manual(name = "ID", values = colorPal)
  }
  
  locP = locP +
    facet_wrap(locFrame, ncol = ncol) +
    coord_fixed(ratio=1) +
    scale_x_continuous(limits = xlim, expand = c(0,0)) +
    scale_y_continuous(trans = "reverse", limits = ylim, expand = c(0,0)) +
    theme_void() +
    theme(text = element_text(size = 20),
          legend.position = legendPos, 
          panel.border = element_rect(colour="black", 
                                      fill = NA,
                                      linewidth = 1))
  
  return(locP)
}
```

# Introduction

Generate a sequence of concentrically growing waves with random duration placed randomly in X/Y/T.

# Collective events

Create an `arcosTS` object. The `eventid` column corresponds to an ID of a synthetic event. The `id` column is the ID of an object.

```{r collCreate}
# create events
nevents = 10L
maxt = 25L
maxx = 20L
maxy = 20L
maxdur = 5L

ts = ARCOS::genRandSynth2D(nevents = nevents,
                           maxt = maxt,
                           maxx = maxx,
                           maxy = maxy,
                           maxdur = maxdur,
                           inSeed = 1)
```

```{r collPrint, echo=F, results="asis"}
knitr::kable(head(ts))
```

```{r collPlot, echo = F, fig.width=10, fig.height=10, warning=FALSE}
# For visualisation, expand the t column to include all frames, even empty ones.
setkey(ts, t)
ts = ts[setkey(ts[,
                  .(seq(min(t, na.rm = T),
                        max(t, na.rm = T),
                        1))],
               V1)]

# reapply attributes
ARCOS::arcosTS(dt = ts,
               colPos = c("x", "y"), 
               colIDobj = "id",
               colFrame = "t")

vEventID = unique(ts$eventid)[!is.na(unique(ts$eventid))]
names(myColPal) = vEventID

myPlotBinTS(ts, 
            colorVar = "eventid",
            colorPal = myColPal,
            plotType = "tile", 
            legendPos = "right",
            ncol = 5, 
            xlim = c(-1, maxx+1), 
            ylim = c(maxy+1, -1))
```

# Identification of collective events

Identify and track collective events. The `collid` column is the result of the tracking algorithm. 

Note that the events can overlap, therefore the ID of collective event (column `collid`) from the tracking algorithm may differ from the original event id (column `eventid`).

```{r collID, echo = T}
tcoll = ARCOS::trackColl(ts[complete.cases(ts)], 
                         eps = 2)
```

```{r collOutPrint, echo=F, results="asis"}
knitr::kable(head(tcoll))
```

```{r collOutPlot, echo = F, fig.width=10, fig.height=10, warning=FALSE}
# For visualisation, expand t column to include all frames, even empty ones.
setkey(tcoll, t)
tcoll = tcoll[setkey(tcoll[,
                           .(seq(min(t, na.rm = T),
                                 max(t, na.rm = T),
                                 1))],
                     V1)]

# reapply attributes
ARCOS::arcosTS(dt = tcoll,
               colPos = c("x", "y"), 
               colIDobj = "id",
               colFrame = "t", 
               colIDcoll = "collid",
               fromColl = TRUE)

vCollID = unique(tcoll$eventid)[!is.na(unique(tcoll$eventid))]
names(myColPal) = vCollID

myPlotBinTS(tcoll, 
            colorVar = "collid",
            colorPal = vCollID,
            legendPos = "right",
            plotType = "tile", 
            ncol = 5, 
            xlim = c(-1, maxx+1), 
            ylim = c(maxy+1, -1))
```

# Save frames

Save facets as individual frames in PNG files. Can be further converted to an animation.

```{r collOutSaveFrames, fig.width=3, fig.height=3, eval = F}
# Create output directory for saving PNG frames
if (lPar$saveFrames) {
  dir.create(file.path(lPar$dirCore,
                       lPar$dirFramesOut), 
             recursive = TRUE, showWarnings = F)
}

vCollID = unique(tcoll$collid)[!is.na(unique(tcoll$collid))]
names(myColPal) = vCollID

if (lPar$saveFrames) {
  for (ii in seq_len(maxt)) {
    locFrame = tcoll[t == ii]
    
    pOut = ggplot(locFrame,
                  aes(x = x,
                      y = y)) +
      theme_void() +
      theme(text = element_text(size = 20),
            legend.position = "none", 
            panel.border = element_rect(colour="black", 
                                        fill = NA,
                                        linewidth = 1),
            panel.background = element_rect(fill = "grey90")) +
      geom_text(x=0, y=0, 
                label=sprintf("%d", ii))
    
    # Generate an empty plot, if data does not exists in the frame.
    if (sum(complete.cases(locFrame)) > 0) {
      pOut = pOut +
        geom_tile(aes(fill = as.factor(get("collid")))) +
        scale_fill_manual(name = "ID", 
                          values = myColPal,
        ) +
        coord_fixed(ratio=1) +
        scale_x_continuous(limits = c(-1, maxx), expand = c(0,0)) +
        scale_y_continuous(trans = "reverse", 
                           limits = c(maxy, -1), expand = c(0,0))
    } 
    
    locFname = file.path(lPar$dirCore,
                         lPar$dirFramesOut,
                         sprintf("frame-%04d.png", ii))
    
    ggsave(filename = locFname, plot = 
             pOut, width = 3, height = 3)
    
  }
}


```

# Create animation

Convert a sequence of PNG files into an animated GIF using ImageMagick's `convert` and/or into an MP4 movie using `ffmpeg`.

```{r collOutSaveAnim, eval = F}
# Use ImageMagick to create an animated GIF
vFrames <- sort(
  list.files(
    file.path(lPar$dirCore,
              lPar$dirFramesOut), 
    "^.*\\.png$", 
    full.names = T))

system2("convert", 
        args = c(vFrames, 
                 c("-loop", "0", 
                   file.path(lPar$dirCore,
                             lPar$dirFramesOut, 
                             "frame-anim.gif"))))

# Using ffmpeg to create mp4
system2("ffmpeg", 
        args = c("-y -framerate", 5, 
                 "-i", sprintf("%s/frame-%%04d.png",
                               file.path(lPar$dirCore,
                                         lPar$dirFramesOut)),
                 "-vcodec libx264 -s 560x420 -pix_fmt yuv420p",
                 file.path(lPar$dirCore,
                           lPar$dirFramesOut, 
                           "frame-anim.mp4")))
```
