---
title: "ARCOS detect from images"
output: 
  rmarkdown::html_vignette:
    toc: true 
vignette: >
  %\VignetteIndexEntry{ARCOS detect from images}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup}
library(ARCOS)
library(ggplot2)

# Custom functions

myPlotBinRasterTS <- function(objTS, xlim = c(0,65), ylim = c(65,0)) {

  ggplot(objTS,
       aes(x = x,
           y = y)) +
  geom_raster(aes(fill = as.factor(m))) +
  scale_fill_manual(name = "Meas.",
                    values = c("grey80",
                                "grey20")) +
  facet_wrap(~ frame, ncol = 4) +
  coord_fixed(ratio=1) +
  scale_x_continuous(limits = xlim) +
  scale_y_continuous(trans = "reverse", limits = ylim) +
  xlab("x") +
  ylab("y") +
  theme_minimal()
}

myPlotRasterColl <- function(objColl, xlim = c(0,65), ylim = c(65,0)) {
  ggplot(objColl,
       aes(x = x,
           y = y)) +
  geom_raster(aes(fill = as.factor(collid))) +
  scale_fill_discrete(name = "ID coll.") +
  facet_wrap(~ frame) +
  coord_fixed(ratio=1) +
  scale_x_continuous(limits = xlim) +
  scale_y_continuous(trans = "reverse", limits = ylim) +
  xlab("x") +
  ylab("y") +
  theme_minimal()
}
```

# Introduction

Here we demonstrate tracking of collective events from a sequence of binary images. Each pixel in the image is treated as a separate object, to which an `objID` number is assigned. The `objID` identifier is the same for objects with the same X/Y position in subsequent frames.

Pixel values, the *measurement*, assume values 0 or 1, which correspond to an inactive or active object, respectively. Objects with value 1 are *active* and our goal is to detect and track a collective activation of all such objects in all frames of the time sequence. 

# Growing circle

Here we detect and track a concentrically growing cluster of active objects directly from a sequence of 12 binary PNG images at 64-by-64 pixel resolution.

## Read data from images

We use the `loadDataFromImages` function to read data from PNG images. The function returns an `arcosTS` object, which is a `data.table` with additional attributes that specify position, measurement, and object ID columns.

Since images are binary, we set the `thres` parameter to `-1` to load all data, zeroes and ones, without thresholding.

```{r,echo=T}
dtIm = ARCOS::loadDataFromImages(file.path(system.file("testImagePatterns/concentricGrowth",
                                                       package="ARCOS"), 
                                           "png_64"),
                                 "*.png", 
                                 thres = -1)
```


The final long-format input data with active/inactive objects. Columns:

- `x` and `y` correspond to X/Y coordinates of an object,
- `m` contains binarised measurement $\{0,1\}$ that corresponds to inactive/active objects, respectively. For identification of collective events we will only use *active* objects, i.e. $m > 0$,
- `objID` holds an object identifier, which should be *at least* unique within a single time frame,
- `time` indicates the time frame number.

```{r echo=F, results="asis"}
knitr::kable(head(dtIm))
```

## Time sequence

Here we plot the time sequence with a growing concentric circle. Each frame (time point) consists of a matrix of 64x64 objects, where each object can assume a value of 0 (inactive) or 1 (active). In this example objects **do not** change their positions or identities across frames. In general, both positions and object identifiers may change between frames.

```{r,echo=F, fig.width=6, fig.height = 5, caption="Concentrically growing circle"}
myPlotBinRasterTS(dtIm)
```


## Detection and tracking 

We use the `ARCOS::trackColl` function to identify collective events in frames and to link them between frames.

```{r, echo = T}
dtColl = ARCOS::trackColl(dtIm[m>0])
```

The result from tracking of collective events is a long-format `data.table` with columns:

- `time` with the frame number,
- `objID` with an identifier of an object involved in a collective event,
- `collID` with an identifier of a collective event that is unique across the entire frame sequence.

```{r echo=F, results="asis"}
knitr::kable(head(dtColl))
```

## Visualisation

Here we display frames only with collective events. The algorithm identified a single event in 10 subsequent frames:

```{r, echo = F, fig.width=6, fig.height = 5, caption="Collective events"}
myPlotRasterColl(dtColl)
```

# Moving circle

Detect and track a moving cluster of active objects directly from a sequence of 16 binary PNG images at 64-by-64 pixel resolution.

```{r,echo=F, fig.width=6, fig.height = 5, caption="Concentrically growing circle"}
dtIm = ARCOS::loadDataFromImages(file.path(system.file("testImagePatterns/movingCircle",
                                                       package="ARCOS"), 
                                           "png_64"),
                                 "*.png", 
                                 thres = -1)
myPlotBinRasterTS(dtIm)
```

```{r, echo = F, fig.width=6, fig.height = 5, caption="Collective events"}
dtColl = ARCOS::trackColl(dtIm[m>0])

myPlotRasterColl(dtColl)
```

# Split circle

Detect and track a cluster of active objects that splits into two parts. Analysis directly from a sequence of 15 binary PNG images at 64-by-64 pixel resolution.

The analysis should consider everything as a single cluster even after the split.

```{r,echo=F, fig.width=6, fig.height = 5, caption="Concentrically growing circle"}
dtIm = ARCOS::loadDataFromImages(file.path(system.file("testImagePatterns/splitCircle",
                                                       package="ARCOS"), 
                                           "png_64"),
                                 "*.png", 
                                 thres = -1)
myPlotBinRasterTS(dtIm)
```

```{r, echo = F, fig.width=6, fig.height = 5, caption="Collective events"}
dtColl = ARCOS::trackColl(dtIm[m>0])

myPlotRasterColl(dtColl)
```

# Moving multiple circles

Detect and track multiple moving clusters of active objects directly from a sequence of 9 binary PNG images at 64-by-64 pixel resolution.

```{r,echo=F, fig.width=6, fig.height = 5, caption="Concentrically growing circle"}
dtIm = ARCOS::loadDataFromImages(file.path(system.file("testImagePatterns/movingMulti",
                                                       package="ARCOS"), 
                                           "png_64"),
                                 "*.png", 
                                 thres = -1)
myPlotBinRasterTS(dtIm)
```
```{r, echo = F, fig.width=6, fig.height = 5, caption="Collective events"}
dtColl = ARCOS::trackColl(dtIm[m>0])

myPlotRasterColl(dtColl)
```
