---
title: "ARCOS demo of unit tests"
output:   
  rmarkdown::html_vignette:
    toc: true 
vignette: >
  %\VignetteIndexEntry{ARCOS demo of unit tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup}
library(ARCOS)
library(data.table)
library(ggplot2)
library(ggthemes)

library(testthat)

## Custom functions

# Wrapper function for testing
myTest = function(inDTcalc, inFtrue, inDir = "testdata") {
  
  resTest = testthat::test_that("test chunk", {
    locDTtrueRes = fread(file.path(system.file(inDir, 
                                               package="ARCOS"),
                                   inFtrue))
    attr(inDTcalc, "sorted") = NULL
    attr(inDTcalc, "class") = c("data.table", "data.frame")
    
    if ("clTrackID" %in% names(locDTtrueRes)) setnames(inDTcalc, "collid", "clTrackID")
    expect_equal(inDTcalc, 
                 locDTtrueRes)
  })
}
```

# Introduction

Demonstration of the ARCOS algorithm on synthetic data used for unit testing.

# Link 1 frame

Only spatial clusters in consecutive frames are linked.

## Test 1 - 1 central

A single object that is active at frames 2, [4,5], and [7,9]. There are gaps of inactivity at frames 3 and 6.

```{r, echo = T, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", package="ARCOS"), "1central_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

The parameter `nPrev = 1L` tells the tracking algorithm to link events only from consecutive frames, i.e. it *looks back* only 1 frame. Hence, clustering will yield 3 events at frames 2, [4,5], [7,8,9].

```{r, echo = T, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```


```{r, echo = F, results="asis"}
myTest(dcoll[,
             .(time, trackID, collid)],
       "1central_res.csv")
```

## Test 2 - 3 spreading

Consider 7 objects that become subsequently active every 2 frames. It mimics an activity wave spreading from object #4 to neighbouring objects.

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "3spreading_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

By linking events that are 1 frame apart (parameter `nPrev = 1L`), the tracking algorithm identifies 3 collective events.

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
             .(time, trackID, collid)],
       "3spreading_res.csv")
```

## Test 3 - 5 overlapping

Consider two objects 2 spatial units apart that beocme active at overlapping time points.

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "5overlapping_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(time, trackID, collid)],
       "5overlapping_res.csv")
```

## Test 4 - 6 overlapping


```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "6overlapping_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(time, trackID, collid)],
       "6overlapping_res.csv")
```

## Test 5 - 1 central growing

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "1centralGrowing_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(time, trackID, collid)],
       "1centralGrowing_res.csv")
```

## Test 6 - 2 central growing

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2centralGrowing_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(time, trackID, collid)],
       "2centralGrowing_res.csv")
```


## Test 7 - 2 with 1 common symmetric

This test addresses a problem of two different activation events (objects #1 and 2) that spread to a common, equidistant neighbour (object #3).

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2with1commonSym_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

Since there's no obvious way to treat this symmetric case, the algorithm assumes that the common neighbour becomes active due to one of the initiators. Here, the activation wave #2 from object #2 spreads to object #3, while the activation wave #1 from object #1 is confined only to that object.

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(time, trackID, collid)],
       "2with1commonSym_res.csv")
```

## Test 8 - 2 with 1 common asymmetric

A similar situation to the previous case but object #3 is no longer equidistant to objects #1 and 2. Instead, it is closer to object #1.

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2with1commonAsym_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```
Since the neighbourhood cut-off is 1 distance unit (parameter `eps`), the collective activation #1 from object #1 spreads to object #3.

```{r, echo = T, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(time, trackID, collid)],
       "2with1commonAsym_res.csv")
```


# Multiple new objects

## Test 1 - simultaneous

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "multipleSimulNewObjects_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "multipleSimulNewObjects_out.csv")
```

## Test 2 - 4 new objects at once after 1

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "multipleSubseq4NewObjectsAfter1_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "multipleSubseq4NewObjectsAfter1_out.csv")
```

## Test 3 - 3 new objects at once after 2

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "multipleSubseq3NewObjectsAfter2_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "multipleSubseq3NewObjectsAfter2_out.csv")
```


## Test 4 - 4 new objects at once after 2

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "multipleSubseq4NewObjectsAfter2_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "multipleSubseq4NewObjectsAfter2_out.csv")
```


## Test 5 - 4 subsequently

```{r, echo = F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "multipleSubseqNewObjects_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)
ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "multipleSubseqNewObjects_out.csv")
```

# Split, cross, merge

## Test 1 - split from single

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "1objSplit_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "1objSplit_res.csv")
```

## Test 2 - split from 2 objects

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2objSplit_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "2objSplit_res.csv")
```

## Test 3 - cross 2 objects

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2objCross_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "2objCross_res.csv")
```

## Test 4 - cross 2 objects with common

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2objCrossCommon_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "2objCrossCommon_res.csv")
```

## Test 5 - merge & split 2 objects with common

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2objMergeSplitCommon_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "2objMergeSplitCommon_res.csv")
```

## Test 6 - merge & split 2 objects crossing

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2objMergeSplitCross_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "2objMergeSplitCross_res.csv")
```

## Test 7 - merge & split 2 objects near

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "2objMergeSplitNear_in.csv"),
                              colPos = "pos",
                              col = list(Frame = "t",
                                         IDobj = "id",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts, 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 1L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(t, id, collid)],
       "2objMergeSplitNear_res.csv")
```

# Link 2 frames

Spatial clusters are linked 2 frames back, thus a one-frame-gap is allowed in a collective event.

## Test 1 - 1 central

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", package="ARCOS"), "1central_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")

ARCOS::plotTracks(dts, size = 3)

```
Here parameter `nPrev = 2L`, which links events from two consecutive frames, i.e. it *looks back* 2 frames. Hence, clustering will yield 1 continuous events.

```{r, echo = T, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 2L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
             .(time, trackID, collid)],
       "1central2prev_res.csv")
```

## Test 2 - 3 spreading

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "3spreading_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 2L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
             .(time, trackID, collid)],
       "3spreading2prev_res.csv")
```

## Test 3 - 5 overlapping

```{r, echo=F, fig.width=6, fig.height=5}
dts = ARCOS::loadDataFromFile(file.path(system.file("testdata", 
                                                    package="ARCOS"), 
                                        "5overlapping_in.csv"),
                              colPos = "x",
                              colMeas = "m",
                              col = list(Frame = "time",
                                         IDobj = "trackID",
                                         RT = NULL,
                                         IDcoll = NULL),
                              interVal = 1L,
                              interType = "fixed")


ARCOS::plotTracks(dts[m>0], size = 3)
```

```{r, echo = F, fig.width=6, fig.height=5}
dcoll = ARCOS::trackColl(obj = dts[m>0], 
                         eps = 1.0, 
                         minClSz = 1L, 
                         nPrev = 2L,
                         deb = F)

ARCOS::plotTracks(dcoll, size = 3)
```

```{r, echo = F, results="asis"}
myTest(dcoll[,
              .(time, trackID, collid)],
       "5overlapping2prev_res.csv")
```
