---
title: "Advanced usage of ARCOS"
output: 
  rmarkdown::html_vignette:
    toc: true 
vignette: >
  %\VignetteIndexEntry{Advanced usage of ARCOS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r setup}
library(ARCOS)
library(data.table)
```

# Introduction

At its core, the tracking algorithm starts with spatial clustering in the first frame with objects using `dbscan` algorithm. Objects from subsequent frames are added to existing clusters based on their threshold distance. Objects that cannot be added to any of the existing clusters are again spatially clustered and form potential *seeds* of new clusters. The entire procedure is repeated. 

The application of this clustering procedure to collective activation events in biological systems requires identification of *active* objects, i.e. objects that will be passed to the clustering algorithm. In practice the single-cell activity over time needs to be thresholded and binarised. ARCOS offers several approaches to perform such approaches that will be covered below.

# Basic example

In this example 4 distinct objects are moving in 1 dimension over 5 time points. We aim to identify clusters of objects moving close to each other.

## Time sequence

The minimal data in the long format consists of 3 columns:

- `frame` with the frame number that corresponds to the time point,
- `objid` with the unique identifier of every object,
- `x` with the position of the object.


```{r echo = T, results="asis"}
dts = data.table(frame = c(1, 1, 2, 2, 2, 3, 3, 3, 3, 4, 4, 4, 5, 5),
                 objid = c(1, 2, 1, 2, 3, 1, 2, 3, 4, 1, 2, 4, 1, 4),
                 x = c(1, 3, 1.2, 2.5, 3.5, 0.9, 2.6, 2.9, 3.2, 1.1, 2.8, 3.1, 1, 3))

knitr::kable(dts)
```

Initiate an `arcosTS` object. Specify the names of frame, object id, and positions columns. The function simply adds attributes to the existing data.table object.

```{r, echo = T}
library(ARCOS)

ARCOS::arcosTS(dt = dts, 
               colPos = "x", 
               col = list(Frame = "frame", 
                          RT = NULL, 
                          IDobj = "objid", 
                          IDcoll = NULL), 
               interVal = 1, 
               interType = "f")
```

Plot the time series. Each object has a distinct identifier represented by a different colour in the plot:

```{r, echo = F, fig.width=5, fig.height=5, caption="Visualisation of object traces over time"}
plotTracks(dts)
```

## Detection and tracking

In this step 3 objects on the top are grouped into a single collective event that spans 5 frames. A single object on the bottom forms a  single-object event. 

The most important parameter of the `trackColl` function is the search radius `eps`, which sets the distance for:

- the `dbscan` spatial clustering in a single time frame,
- possible objects that can be part of collective events identified in previous frame(s).

The minimum size of the spatial cluster is set using the `minClSz` parameter, which is also passed to `dbscan`. The parameter `nPrev` determines the number of previous frames that are searched for collective events in order to match them to objects in the current frame.

```{r, echo = T}
dcoll = ARCOS::trackColl(dts)
```

The output contains 3 columns with the frame number, object identifier, and the calculated identifier of the collective event:

```{r echo=F, results="asis"}
knitr::kable(dcoll)
```

## Visualisation

Plot:

Each trace is assigned an identifier of the collective event, which is represented by the shape of the point in the plot:

```{r, echo = F, fig.width=5, fig.height=5, caption="Visualisation of collective events over time"}
plotTracks(dcoll)
```

The algorithm with the default search radius `eps=1.0` has identified two collective events. One is an event with only a single object, the latter is an event that consists of 1 to 3 objects at different points in time.

# Single-cell dynamics

TODO
